### 2009-04-28 doc/internal_notes/dmc/dmc.tex
Reorganizing doc catalogue and enabling make doc

  class DataPointCustomDirect : public DataPointDirect {
   public:
    DataPointCustomDirect(const URL& url);
    virtual ~DataPointCustomDirect();
    virtual bool start_reading(DataBufferPar& buffer);
    virtual bool start_writing(DataBufferPar& buffer,
                               DataCallback *space_cb = NULL);
    virtual bool stop_reading(void);
    virtual bool stop_writing(void);
    virtual bool analyze(analyze_t& arg);
    virtual bool check(void);
    virtual bool remove(void);
    virtual bool list_files(std::list<FileInfo>& files, bool resolve = true);
  };

@@

  class DataPointCustom2 : public DataPointIndex {
   public:
    DataPointCustom2(const URL& url);
    ~DataPointCustom2() {};
    virtual bool meta_resolve(bool source);
    virtual bool meta_preregister(bool replication, bool force = false);
    virtual bool meta_postregister(bool replication);
    virtual bool meta_preunregister(bool replication);
    virtual bool meta_unregister(bool all);
    virtual bool list_files(std::list<FileInfo> &files, bool resolve = true);
  };

>>>>

  class DataPointCustomDirect : public DataPointDirect {
   public:
    DataPointCustomDirect(const URL& url);
    virtual ~DataPointCustomDirect();
    virtual DataStatus StartReading(DataBuffer& buffer);
    virtual DataStatus StartWriting(DataBuffer& buffer,
                                    DataCallback *space_cb = NULL);
    virtual DataStatus StopReading();
    virtual DataStatus StopWriting();
    virtual DataStatus Check();
    virtual DataStatus Remove();
    virtual DataStatus ListFiles(std::list<FileInfo>& files,
                                 bool long_list = false, bool resolve = false);
  };

@@

  class DataPointCustom2 : public DataPointIndex {
   public:
    DataPointCustom2(const URL& url);
    ~DataPointCustom2() {};
    virtual DataStatus Resolve(bool source);
    virtual DataStatus PreRegister(bool replication, bool force = false);
    virtual DataStatus PostRegister(bool replication);
    virtual DataStatus PreUnregister(bool replication);
    virtual DataStatus Unregister(bool all);
    virtual DataStatus ListFiles(std::list<FileInfo>& files,
                                 bool long_list = false, bool resolve = false);
  };

### 2009-04-28 doc/manuals/ws-quick-guide/ws-quick-guide.tex
Reorganizing doc catalogue and enabling make doc

Now you may use the command line utility ``\texttt{arcinfo}'' to obtain a service
description. Make sure user key and certificate and CA certificate(s) are
readable from account you use, and run something like:

\begin{lstlisting}
./arcinfo -d VERBOSE -C $HOME/usercert.pem -K $HOME/userkey.pem
 -A /etc/grid-security/certificates https://localhost:60000/arex 2>error.log
\end{lstlisting}

This should produce XML output describing resource A-REX represents.
Listing~\ref{lst:arcinfo} shows an example of proper output. In case of error see
\texttt{error.log} file and report problems to ARC development team. Include
content of \texttt{error.log} and server log.

\begin{lstlisting}[caption={Example of a good arcinfo output},label=lst:arcinfo]
<n:nordugrid xmlns:n="urn:nordugrid" xmlns:M0="urn:Mds"
xmlns:nc0="urn:nordugrid-cluster">
  <nc0:name>mobile2.home.net</nc0:name>
  <nc0:aliasname>MINIMAL Computing Element</nc0:aliasname>
  <nc0:comment>This is a minimal out-of-box CE setup</nc0:comment>
  <nc0:issuerca>/O=Grid/O=Test/CN=CA</nc0:issuerca>
  <nc0:issuerca-hash>4457e417</nc0:issuerca-hash>
  <nc0:trustedca>/O=Grid/O=NorduGrid/CN=NorduGrid Certification
Authority</nc0:trustedca>
  <nc0:trustedca>/O=Grid/O=Test/CN=CA</nc0:trustedca>
  <nc0:contactstring>gsiftp://mobile2.home.net:2811/jobs</nc0:contactstring>
  <nc0:lrms-type>fork</nc0:lrms-type>
  <nc0:architecture>i686</nc0:architecture>
  <nc0:homogeneity>TRUE</nc0:homogeneity>
  <nc0:nodeaccess>inbound</nc0:nodeaccess>
  <nc0:nodeaccess>outbound</nc0:nodeaccess>
  <nc0:totalcpus>1</nc0:totalcpus>
  <nc0:usedcpus>0</nc0:usedcpus>
  <nc0:cpudistribution>1cpu:1</nc0:cpudistribution>
  <nc0:prelrmsqueued>0</nc0:prelrmsqueued>
  <nc0:totaljobs>0</nc0:totaljobs>
  <nc0:sessiondir-free>8469</nc0:sessiondir-free>
  <nc0:sessiondir-total>43865</nc0:sessiondir-total>
  <nc0:sessiondir-lifetime>10080</nc0:sessiondir-lifetime>
  <M0:validfrom>20080220142836Z</M0:validfrom>
  <M0:validto>20080220143036Z</M0:validto>
  <nq0:name xmlns:nq0="urn:nordugrid-queue" name="fork">
    <nq0:name>fork</nq0:name>
    <nq0:status>inactive, grid-manager is down</nq0:status>
    <nq0:comment>This queue is nothing more than a fork host</nq0:comment>
    <nq0:schedulingpolicy>FIFO</nq0:schedulingpolicy>
    <nq0:homogeneity>TRUE</nq0:homogeneity>
    <nq0:nodecpu>Intel(R) Celeron(R) M CPU        420  @ 1.60GHz @ 1596.048
MHz</nq0:nodecpu>
    <nq0:architecture>i686</nq0:architecture>
    <nq0:maxcputime>unlimited</nq0:maxcputime>
    <nq0:maxwalltime>unlimited</nq0:maxwalltime>
    <nq0:running>0</nq0:running>
    <nq0:gridrunning>0</nq0:gridrunning>
    <nq0:localqueued>0</nq0:localqueued>
    <nq0:gridqueued>0</nq0:gridqueued>
    <nq0:prelrmsqueued>0</nq0:prelrmsqueued>
    <nq0:totalcpus>1</nq0:totalcpus>
    <IM0:validfrom>20080220142836Z</M0:validfrom>
    <M0:validto>20080220143036Z</M0:validto>
    <nig0:name xmlns:nig0="urn:nordugrid-info-group" name="jobs">
      <nig0:name>jobs</nig0:name>
      <M0:validfrom>20080220142836Z</M0:validfrom>
      <M0:validto>20080220143036Z</M0:validto>
      <nj0:globalid xmlns:nj0="urn:nordugrid-job"
name="gsiftp://mobile2.home.net:2811/jobs/636312034687631804
289383">

<nj0:globalid>gsiftp://mobile2.home.net:2811/jobs/636312034687631804289383</nj0:
globalid>
        <nj0:globalowner>/O=Grid/O=Test/CN=user</nj0:globalowner>
        <nj0:jobname>TEST</nj0:jobname>
        <nj0:execcluster>mobile2.home.net</nj0:execcluster>
        <nj0:execqueue>fork</nj0:execqueue>
        <nj0:submissionui>127.0.0.1:59790</nj0:submissionui>
        <nj0:submissiontime>20080220005243Z</nj0:submissiontime>
        <nj0:sessiondirerasetime>20080227005843Z</nj0:sessiondirerasetime>
        <nj0:completiontime>20080220005843Z</nj0:completiontime>
        <nj0:cpucount>1</nj0:cpucount>
        <nj0:comment>GM: The grid-manager is down</nj0:comment>
        <nj0:usedcputime>0</nj0:usedcputime>
        <nj0:usedwalltime>0</nj0:usedwalltime>
        <nj0:errors>Job submission to LRMS failed</nj0:errors>
        <nj0:status>FAILED</nj0:status>
        <nj0:rerunable>SUBMIT</nj0:rerunable>
        <M0:validfrom>20080220142836Z</M0:validfrom>
        <M0:validto>20080220143036Z</M0:validto>
      </nj0:globalid>
    </nig0:name>
    <nig0:name xmlns:nig0="urn:nordugrid-info-group" name="users">
      <nig0:name>users</nig0:name>
      <M0:validfrom>20080220142836Z</M0:validfrom>
      <M0:validto>20080220143036Z</M0:validto>
    </nig0:name>
  </nq0:name>
</n:nordugrid>
\end{lstlisting}

Please note that you can run similar \texttt{arcinfo} request against any ARC1
service except Echo service. Output should always be XML description of the service.

A-REX accepts jobs described in JSDL language. Example JSDL jobs are provided in
\verb|$ARC_LOCATION/share/doc/| in files \verb|jsdl_simple.xml| and
\verb|jsdl_stage.xml|. To submit job to A-REX service one may use
\texttt{arcsub} command:

\begin{lstlisting}
$ARC_LOCATION/bin/arcsub https://localhost:60000/arex
 /usr/local/share/doc/arc/jsdl_simple.xml id.xml
\end{lstlisting}

@@

\begin{lstlisting}
$ARC_LOCATION/bin/arcstat id.xml 2>/dev/null
Job status: Running/Submitting

$ARC_LOCATION/bin/arcstat id.xml 2>/dev/null
Job status: Running/Finishing

$ARC_LOCATION/bin/arcstat id.xml 2>/dev/null
Job status: Finished/Finished
\end{lstlisting}

Full set of A-REX client tools consists of \texttt{arcsub}, \texttt{arcstat},
\texttt{arckill}, \texttt{arcget} and \texttt{arcclean} commands.
For more information please see man pages ot those utilities.

>>>>

Now you may use the command line utility ``\texttt{arcinfo}'' to obtain a service
description. You can do something like:

\begin{lstlisting}
./arcinfo -c ARC1:https://localhost:60000/arex -l
\end{lstlisting}

This should produce a description list~\ref{lst:arcinfo} of the resources A-REX
represents. Below you can see an example of proper output.

\begin{lstlisting}[caption={Example of proper arcinfo output},label=lst:arcinfo]
Cluster: localhost
 Health State: ok

Location information:

Domain information:

Service information:
 Service Name: MINIMAL Computing Element
 Service Type: org.nordugrid.arex

Endpoint information:
 URL: https://localhost:60000/arex
 Capabilities:
  executionmanagement.jobexecution
 Technology: webservice
 Interface Name: OGSA-BES
 Supported Profiles:
  WS-I 1.0
  HPC-BP
 Implementor: NorduGrid
 Implementation Name: A-REX
 Implementation Version: 0.9
 QualityLevel: development
 Health State: ok
 Serving State: production
 Issuer CA: /O=Grid/O=NorduGrid/CN=NorduGrid Certification Authority
 Trusted CAs:
  /C=BE/O=BELNET/OU=BEGrid/CN=BEGrid CA/emailAddress=gridca@belnet.be
  /C=FR/O=CNRS/CN=CNRS2-Projets
  /DC=org/DC=ugrid/CN=UGRID CA
  /C=BR/O=ICPEDU/O=UFF BrGrid CA/CN=UFF Brazilian Grid Certification Authority
  /C=DE/O=DFN-Verein/OU=DFN-PKI/CN=DFN-Verein PCA Grid - G01
  /C=PT/O=LIPCA/CN=LIP Certification Authority
  /C=FR/O=CNRS/CN=GRID-FR
  /C=FR/O=CNRS/CN=CNRS2
  /C=TR/O=TRGrid/CN=TR-Grid CA
  /C=NL/O=NIKHEF/CN=NIKHEF medium-security certification auth
  /DC=org/DC=DOEGrids/OU=Certificate Authorities/CN=DOEGrids CA 1
  /DC=ch/DC=cern/CN=CERN Trusted Certification Authority
  /C=AU/O=APACGrid/OU=CA/CN=APACGrid/emailAddress=camanager@vpac.org
  /C=IE/O=Grid-Ireland/CN=Grid-Ireland Certification Authority
  /O=Grid/O=NorduGrid/CN=NorduGrid Certification Authority
  /DC=RO/DC=RomanianGRID/O=ROSA/OU=Certification Authority/CN=RomanianGRID CA
  /DC=bg/DC=acad/CN=BG.ACAD CA
  /C=MX/O=UNAMgrid/OU=UNAM/CN=CA
  /C=GR/O=HellasGrid/OU=Certification Authorities/CN=HellasGrid Root CA 2006
  /C=CL/O=REUNACA/CN=REUNA Certification Authority
  /DC=org/DC=balticgrid/CN=Baltic Grid Certification Authority
  /C=IT/O=INFN/CN=INFN CA
  /DC=me/DC=ac/DC=MREN/CN=MREN-CA
  /C=FR/O=CNRS/CN=CNRS-Projets
  /C=DE/O=DFN-Verein/OU=DFN-PKI/CN=DFN-Verein User CA Grid - G01
  /C=UK/O=eScienceCA/OU=Authority/CN=UK e-Science CA
  /C=RS/O=AEGIS/CN=AEGIS-CA
  /C=SI/O=SiGNET/CN=SiGNET CA
  /C=VE/O=Grid/O=Universidad de Los Andes/OU=CeCalCULA/CN=ULAGrid Certification Authority
  /DC=ORG/DC=SEE-GRID/CN=SEE-GRID CA
  /C=CH/O=Switch - Teleinformatikdienste fuer Lehre und Forschung/CN=SWITCH Personal CA
  /C=RU/O=RDIG/CN=Russian Data-Intensive Grid CA
  /C=HU/O=KFKI RMKI CA/CN=KFKI RMKI CA
  /C=JP/O=KEK/OU=CRC/CN=KEK GRID Certificate Authority
  /DC=EDU/DC=UTEXAS/DC=TACC/O=UT-AUSTIN/CN=TACC Root CA
  /C=AT/O=AustrianGrid/OU=Certification Authority/CN=Certificate Issuer
  /C=IL/O=IUCC/CN=IUCC/emailAddress=ca@mail.iucc.ac.il
  /DC=TW/DC=ORG/DC=NCHC/CN=NCHC CA
  /C=KR/O=KISTI/O=GRID/CN=KISTI Grid Certificate Authority
  /DC=LV/DC=latgrid/CN=Certification Authority for Latvian Grid
  /DC=NET/DC=PRAGMA-GRID/CN=PRAGMA-UCSD CA
  /C=CH/O=SwissSign/CN=SwissSign CA (RSA IK May 6 1999 18:00:58)/emailAddress=ca@SwissSign.com
  /C=MA/O=MaGrid/CN=MaGrid CA
  /C=MK/O=MARGI/CN=MARGI-CA
  /C=GR/O=HellasGrid/OU=Certification Authorities/CN=HellasGrid CA 2006
  /C=TH/O=NECTEC/OU=GOC/CN=NECTEC GOC CA
  /C=PL/O=GRID/CN=Polish Grid CA
  /C=UK/O=eScienceRoot/OU=Authority/CN=UK e-Science Root
  /DC=cz/DC=cesnet-ca/CN=CESNET CA
  /C=TW/O=AS/CN=Academia Sinica Grid Computing Certification Authority Mercury
  /DC=es/DC=irisgrid/CN=IRISGridCA
  /C=JP/O=AIST/OU=GRID/CN=Certificate Authority
  /C=JP/O=National Research Grid Initiative/OU=CGRD/CN=NAREGI CA
  /DC=BR/DC=UFF/DC=IC/O=UFF LACGrid CA/CN=UFF Latin American and Caribbean Catch-all Grid CA
  /C=CY/O=CyGrid/O=HPCL/CN=CyGridCA
  /DC=CN/DC=Grid/CN=Root Certificate Authority at CNIC
  /C=AR/O=e-Ciencia/OU=UNLP/L=CeSPI/CN=PKIGrid
  /C=CN/O=HEP/CN=gridca-cn/emailAddress=gridca@ihep.ac.cn
  /C=CA/O=Grid/CN=Grid Canada Certificate Authority
  /CN=SWITCH CA/emailAddress=switch.ca@switch.ch/O=Switch - Teleinformatikdienste fuer Lehre und Forschung/C=CH
  /DC=CN/DC=Grid/DC=SDG/CN=Scientific Data Grid CA
  /C=HU/O=NIIF/OU=Certificate Authorities/CN=NIIF Root CA
  /C=IR/O=IPM/O=IRAN-GRID/CN=IRAN-GRID CA
  /C=FR/O=CNRS/CN=CNRS
  /C=CH/O=Switch - Teleinformatikdienste fuer Lehre und Forschung/CN=SWITCHgrid Root CA
  /C=AM/O=ArmeSFo/CN=ArmeSFo CA
  /C=FR/O=CNRS/CN=GRID2-FR
  /DC=net/DC=ES/O=ESnet/OU=Certificate Authorities/CN=ESnet Root CA 1
  /DC=ch/DC=cern/CN=CERN Root CA
  /DC=IN/DC=GARUDAINDIA/CN=Indian Grid Certification Authority
  /C=DE/O=GermanGrid/CN=GridKa-CA
  /C=SK/O=SlovakGrid/CN=SlovakGrid CA
  /CN=SwissSign Bronze CA/emailAddress=bronze@swisssign.com/O=SwissSign/C=CH
  /DC=EDU/DC=UTEXAS/DC=TACC/O=UT-AUSTIN/CN=TACC Classic CA
  /C=BE/OU=BEGRID/O=BELNET/CN=BEgrid CA
  /CN=SwissSign Silver CA/emailAddress=silver@swisssign.com/O=SwissSign/C=CH
  /C=CH/O=Switch - Teleinformatikdienste fuer Lehre und Forschung/CN=SWITCH Server CA
  /C=PK/O=NCP/CN=PK-GRID-CA
  /C=DE/O=DFN-Verein/OU=DFN-PKI/CN=DFN-Verein Server CA Grid - G01
  /C=HR/O=edu/OU=srce/CN=SRCE CA
 Staging: staginginout
 Job Descriptions:
  ogf:jsdl:1.0

Queue information:
 Mapping Queue: default
 Max Total Jobs: 100
 Max Running Jobs: 10
 Max Waiting Jobs: 99
 Max Pre LRMS Waiting Jobs: 0
 Max User Running Jobs: 5
 Max Slots Per Job: 1
 Doesn't Support Preemption
 Total Jobs: 0
 Running Jobs: 0
 Waiting Jobs: 0
 Suspended Jobs: 0
 Staging Jobs: 0
 Pre-LRMS Waiting Jobs: 0
 Free Slots: 10
 Free Slots With Duration:
  P68Y1M5DT3H14M7S: 10
 Used Slots: 0
 Requested Slots: 0

Manager information:
 Resource Manager: torque
 Doesn't Support Advance Reservations
 Doesn't Support Bulk Submission
 Total Physical CPUs: 10
 Total Logical CPUs: 10
 Total Slots: 10
 Non-homogeneous Resource
 Working area is nor shared among jobs
 Working Area Total Size: 15
 Working Area Free Size: 4
 Working Area Life Time: P7D
 Cache Area Total Size: 15
 Cache Area Free Size: 4

Execution Environment information:
 Execution environment is a physical machine
 Execution environment does not support inbound connections
 Execution environment does not support outbound connections
\end{lstlisting}

Please note that you can run similar \texttt{arcinfo} request against any ARC1
service except echo service.

A-REX accepts jobs described in the JSDL language. Example of JSDL jobs are
provided in \verb|$ARC_LOCATION/share/doc/| in the files \verb|jsdl_simple.xml|
and \verb|jsdl_stage.xml|. To submit job to A-REX service one may use the
\texttt{arcsub} command:

\begin{lstlisting}
$ARC_LOCATION/bin/arcsub -c ARC1:https://localhost:60000/arex -f $ARC_LOCATION/share/doc/arc/jsdl_simple.xml -j id.xml
\end{lstlisting}

If everything goes properly somewhere in it's output there should be a message
"Job submitted!", and a job identifier is obtained which will be stored
in 'id.xml' file. One can then query job state with the \texttt{arcstat} utility:

@@

\begin{lstlisting}
$ARC_LOCATION/bin/arcstat id.xml
Job status: Running/Submitting

$ARC_LOCATION/bin/arcstat id.xml
Job status: Running/Finishing

$ARC_LOCATION/bin/arcstat id.xml
Job status: Finished/Finished
\end{lstlisting}

Some of the of A-REX client tools consists of \texttt{arcsub}, \texttt{arcstat},
\texttt{arckill}, \texttt{arcget} and \texttt{arcclean} commands. For more
information please see the man pages of those utilities.

### 2009-04-28 doc/tech_doc/hed/ARCHED_article.tex
Reorganizing doc catalogue and enabling make doc

The HED is a relatively young framework and there are quite a few rough edges and non-flexible solutions. The situation will hopefully improve with time. We would be grateful for any suggestions how to improve the architecture and the code of the HED. 
Statements like "this is nonsense, I will use Axis instead" are understood but not welcome and are usually reacted adequately.

>>>>

The HED is a relatively young framework and there are quite a few rough edges and non-flexible solutions. The situation will hopefully improve with time. We would be grateful for any constructive comments and suggestions how to improve the architecture and the code of the HED.

### 2009-04-28 doc/tech_doc/hed/counter.tex
Reorganizing doc catalogue and enabling make doc

\title{ARC Counter Library\\
Requirements and Design}
\author{Markus Nord\'en}

>>>>

\title{ARC Counter Library\\
Requirements and Design
\footnote{This document was used as input for discussions during
NorduGrid Technical Meeting in L\"ubeck May 2--4, 2007. For the final
design, see the Doxygen documentation of http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/libs/counter/Counter.h}}
\author{Markus Nord\'en}
